|

### 2020-04-05 paper.tex
Took out plotly/orca.
Needs complicated installation...

\documentclass[12pt,]{article}

@@

\setstretch{1.2}

@@

\usepackage{fixltx2e} % provides \textsubscript

@@

\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}

@@

% use upquote if available, for straight quotes in verbatim environments

@@

% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}

@@

\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,

@@

@@

            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

@@

\setlength{\parskip}{6pt plus 2pt minus 1pt}

@@

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address:
  \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
  Acknowledgments: I am grateful to all those generous people that
  invest their time into open-source software.}\vspace{0.5cm}\\}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{14 December, 2018\\[2\baselineskip]Feedback?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}

\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{url}
\usepackage{array}
\usepackage{setspace}
\usepackage{graphics}
%\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{natbib}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{dcolumn}
\usepackage{lscape}
\usepackage{array}
\usepackage{color}
\usepackage{setspace}

@@

\usepackage[table]{xcolor}

@@

\setlength{\parindent}{0pt} % no indentation
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\usepackage{dcolumn}
\usepackage{color}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle
\begin{abstract}
\noindent\setstretch{1}The present paper provides a template for a
reproducible scientific paper written in R Markdown. Below I outline
some of the ``tricks''/code (e.g., referencing tables, sections etc.) I
had to figure out to produce this document. The underlying files which
produce this document can be downloaded
\href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{here}.
I think I got pretty far but there is always room for improvement and
more automatization, in parallel to the incredible developments in R and
Rstudio (bookdown etc.). I intend to update this file when I discover
more convenient code.\vspace{.8cm}
\end{abstract}

@@

\renewcommand{\baselinestretch}{0.5}

\normalsize
\tableofcontents
\renewcommand{\baselinestretch}{1.1}\normalsize

\section{Why reproducible research (in
R)?}\label{why-reproducible-research-in-r}

@@

\section{Prerequesites}\label{prerequesites}

@@

\begin{itemize}
\tightlist
\item
  \ldots{}install \href{https://www.r-project.org/}{R} and
  \href{https://www.rstudio.com/}{Rstudio} (most recent versions) (R
  Core Team \protect\hyperlink{ref-R2017}{2017}; RStudio Team
  \protect\hyperlink{ref-Rstudio2015}{2015}).
\item
  \ldots{}install \href{https://yihui.name/tinytex/}{tinytex}, a
  lightweight version of Tex Live (Allaire et al.
  \protect\hyperlink{ref-markdown2017}{2017}; Xie
  \protect\hyperlink{ref-tinytex}{2018}\protect\hyperlink{ref-tinytex}{b}).
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \ldots{}install the packages below using the code below (Sievert et
  al. \protect\hyperlink{ref-plotly}{2017}; Xie
  \protect\hyperlink{ref-knitr3}{2014},
  \protect\hyperlink{ref-knitr2}{2015},
  \protect\hyperlink{ref-bookdown2}{2016},
  \protect\hyperlink{ref-bookdown1}{2017},
  \protect\hyperlink{ref-knitr1}{2018}\protect\hyperlink{ref-knitr1}{a};
  Zhu \protect\hyperlink{ref-kableextra}{2017}).
\end{itemize}

@@

\begin{itemize}
\item
  \ldots{}download the 5 input files I created --- \texttt{paper.rmd},
  \texttt{header.tex}, \texttt{references.bib}, \texttt{data.csv} and
  \texttt{american-sociological-association.csl} --- from
  \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this
  folder}. Ignore the other files.
\item
  \ldots{}learn R and read about the other underlying components namely
  \href{https://en.wikipedia.org/wiki/Markdown}{Markdown},
  \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and
  \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

\section{Basics: Input and output
files}\label{basics-input-and-output-files}

@@

\begin{itemize}
\tightlist
\item
  \ldots{}a \texttt{paper.rmd} file (the underlying R Markdown file).
\item
  \ldots{}a \texttt{header.tex} file (a tex file for document
  structure).
\item
  \ldots{}a \texttt{references.bib} file (the bibliography).

  \begin{itemize}
  \tightlist
  \item
    I use paperpile to manage my references and export the \texttt{.bib}
    file into the folder that contains my \texttt{.rmd} file.
  \end{itemize}
\item
  \ldots{}a \texttt{data.csv} file (some raw data).
\item
  \ldots{} a \texttt{american-sociological-association.csl} file that
  defines the style of your bibliography.\footnote{You can download
    various citation style files from this webpage:
    \url{https://github.com/citation-style-language/styles}.}
\end{itemize}

@@

\section{Referencing within your
document}\label{referencing-within-your-document}

@@

\section{Software versioning}\label{software-versioning}

@@

I would recommend to use the command below and copy/paste the output
into the first R chunk in your \texttt{paper.rmd} file. Normally we
would do this when we compile/generate the paper for the last time. For
more advanced tools see
\href{https://rstudio.github.io/packrat/}{packrat}.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{cat}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"#"}\NormalTok{, }\KeywordTok{capture.output}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{()), }\StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\DataTypeTok{collapse =}\StringTok{""}\NormalTok{)) }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # R version 3.5.1 (2018-07-02) 
## # Platform: x86_64-w64-mingw32/x64 (64-bit) 
## # Running under: Windows 10 x64 (build 17134) 
## #  
## # Matrix products: default 
## #  
## # locale: 
## # [1] LC_COLLATE=English_Germany.1252  LC_CTYPE=English_Germany.1252    
## # [3] LC_MONETARY=English_Germany.1252 LC_NUMERIC=C                     
## # [5] LC_TIME=English_Germany.1252     
## #  
## # attached base packages: 
## # [1] stats     graphics  grDevices utils     datasets  methods   base      
## #  
## # loaded via a namespace (and not attached): 
## #  [1] compiler_3.5.1  backports_1.1.2 magrittr_1.5    bookdown_0.7    
## #  [5] rprojroot_1.3-2 tools_3.5.1     htmltools_0.3.6 yaml_2.2.0      
## #  [9] Rcpp_0.12.19    stringi_1.1.7   rmarkdown_1.10  knitr_1.20      
## # [13] stringr_1.3.1   xfun_0.3        digest_0.6.18   evaluate_0.12
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
  \CommentTok{# or use message() instead of cat()}
\end{Highlighting}
\end{Shaded}

\section{Data}\label{data}

\subsection{Import}\label{import}

@@

\subsection{Putting your entire data into the .rmd
file}\label{putting-your-entire-data-into-the-.rmd-file}

@@

\section{Tables}\label{sec:tables}

@@

\subsection{stargazer(): Summary and regression
tables}\label{stargazer-summary-and-regression-tables}

@@

\subsection{kable() and kable\_styling()}\label{kable-and-kable_styling}

@@

\rowcolors{2}{gray!6}{white}

@@

\caption{\label{tab:tab3}Table with kable() and kablestyling()}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\hiderowcolors
\toprule
  & speed & dist\\
\midrule
\showrowcolors
1 & 4 & 2\\
2 & 4 & 10\\
3 & 7 & 4\\
4 & 7 & 22\\
5 & 8 & 16\\
\addlinespace
6 & 9 & 10\\
7 & 10 & 18\\
8 & 10 & 26\\
9 & 10 & 34\\
10 & 11 & 17\\
\bottomrule
\end{tabu}}
\end{table}

\rowcolors{2}{white}{white}

\section{Inline code \& results}\label{inline-code-results}

@@

\section{Figures}\label{figures}

\subsection{R base graphs}\label{r-base-graphs}

@@

\subsection{ggplot2 graphs}\label{ggplot2-graphs}

@@

\subsection{Plotly graphs}\label{plotly-graphs}

Plotly is a popular graph engine that let's you also produce interactive
graphs that you can embed in html webpages or documents (e.g., see
\href{https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/}{here}).
I am a big fan. For some time there was no easy, automatic way to insert
high resolution Plotly graphs into your R Markdown PDF. However, this
changed since Plotly provided Orca, a command line application for
generating static images from Plotly graphs. The installation is a bit
tricky (see here: \url{https://github.com/plotly/orca\#installation})
but once you get it running you can produce beautiful graphs and include
them in your RMarkdown PDF using some simple latex as shown below in
Figure \ref{fig:fig-3}. Potentially, in case you did not install the
command line application this part may fail. If so simply exclude the
chunk and the latex code.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(plotly)}
\NormalTok{p <-}\StringTok{ }\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}
        \DataTypeTok{x=}\OperatorTok{~}\NormalTok{speed, }
        \DataTypeTok{y=}\OperatorTok{~}\NormalTok{dist)}
\KeywordTok{Sys.setenv}\NormalTok{(}\StringTok{'MAPBOX_TOKEN'}\NormalTok{ =}\StringTok{ '12423423'}\NormalTok{) }\CommentTok{# set arbitrary token}
\KeywordTok{orca}\NormalTok{(p, }\StringTok{"plotly-plot.pdf"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]
\centering
\caption{An plotly plot that was exported as PDF with orca before}\label{fig:fig-3}
        \includegraphics[width=0.9\linewidth]{plotly-plot.pdf}
\begin{flushleft}
\end{flushleft}
\end{figure}

\vspace{-1.2cm}

\section{Good practices}\label{good-practices}

@@

  \begin{itemize}
  \tightlist
  \item
    Main file with text/code: ``paper.rmd'', ``report.rmd''
  \item
    Data files: ``data\_xxxxxx.*"
  \item
    Image files: ``fig\_xxxxxx.*"
  \item
    Tables files: ``table\_xxxx.*"
  \item
    etc.
  \item
    Ideally, your filenames will correspond to the names in the paper.
    For instance, Figure 1 in the paper may have a corresponding file
    called \texttt{fig\_1\_xxxxx.pdf}.
  \end{itemize}
\item
  Use the document outline in R studio (Ctrl + Shift + O) when you work
  with R Markdown.
\item
  Name rchunks according to what they do or produce:

@@

\section{Citation styles}\label{citation-styles}

@@

\section{Appendix}\label{appendix}

\subsection{All the code in the paper}\label{all-the-code-in-the-paper}

@@

\KeywordTok{library}\NormalTok{(plotly)}
\NormalTok{p <-}\StringTok{ }\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}
        \DataTypeTok{x=}\OperatorTok{~}\NormalTok{speed, }
        \DataTypeTok{y=}\OperatorTok{~}\NormalTok{dist)}
\KeywordTok{Sys.setenv}\NormalTok{(}\StringTok{'MAPBOX_TOKEN'}\NormalTok{ =}\StringTok{ '12423423'}\NormalTok{) }\CommentTok{# set arbitrary token}
\KeywordTok{orca}\NormalTok{(p, }\StringTok{"plotly-plot.pdf"}\NormalTok{)}

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-markdown2017}{}
Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017.
\emph{Markdown: 'Markdown' Rendering for R}.

\hypertarget{ref-hlavac2013stargazer}{}
Hlavac, Marek. 2013. ``Stargazer: LaTeX Code and Ascii Text for
Well-Formatted Regression and Summary Statistics Tables.'' \emph{URL:
Http://CRAN. R-Project. Org/Package= Stargazer}.

\hypertarget{ref-Kirsop2005-ro}{}
Kirsop, Barbara and Leslie Chan. 2005. ``Transforming Access to Research
Literature for Developing Countries.'' \emph{Serials Review}
31(4):246--55.

\hypertarget{ref-R2017}{}
R Core Team. 2017. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.

\hypertarget{ref-Rstudio2015}{}
RStudio Team. 2015. \emph{RStudio: Integrated Development Environment
for R}. Boston, MA: RStudio, Inc.

\hypertarget{ref-plotly}{}
Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik
Ram, Marianne Corvellec, and Pedro Despouy. 2017. \emph{Plotly: Create
Interactive Web Graphics via 'Plotly.js'}.

\hypertarget{ref-knitr3}{}
Xie, Yihui. 2014. ``Knitr: A Comprehensive Tool for Reproducible
Research in R.'' in \emph{Implementing reproducible computational
research}, edited by V. Stodden, F. Leisch, and R. D. Peng. Chapman;
Hall/CRC.

\hypertarget{ref-knitr2}{}
Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed.
Boca Raton, Florida: Chapman; Hall/CRC.

\hypertarget{ref-bookdown2}{}
Xie, Yihui. 2016. \emph{Bookdown: Authoring Books and Technical
Documents with R Markdown}. Boca Raton, Florida: Chapman; Hall/CRC.

\hypertarget{ref-bookdown1}{}
Xie, Yihui. 2017. \emph{Bookdown: Authoring Books and Technical
Documents with R Markdown}.

\hypertarget{ref-knitr1}{}
Xie, Yihui. 2018a. \emph{Knitr: A General-Purpose Package for Dynamic
Report Generation in R}.

\hypertarget{ref-tinytex}{}
Xie, Yihui. 2018b. \emph{Tinytex: Helper Functions to Install and
Maintain 'Tex Live', and Compile 'Latex' Documents}.

\hypertarget{ref-kableextra}{}
Zhu, Hao. 2017. \emph{KableExtra: Construct Complex Table with 'Kable'
and Pipe Syntax}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  12pt,
]{article}

@@

@@

@@

  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}

@@

% Use upquote if available, for straight quotes in verbatim environments

@@

\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}

@@

\@ifundefined{KOMAClassName}{% if non-KOMA class
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{

@@

  filecolor=Maroon,

@@

  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs

@@

% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

@@

% Set default figure placement to htbp
\def\fps@figure{htbp}

@@

\usepackage[english]{babel}
\usepackage{float}
\usepackage{graphicx}
\usepackage{url}
\usepackage{array}
\usepackage{graphics}
%\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{natbib}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{dcolumn}
\usepackage{lscape}
\usepackage{array}

@@

@@

\setlength{\parindent}{0pt} % no indentation
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
\date{5 April, 2020\\
~\\
Feedback?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}

\begin{document}
\maketitle
\begin{abstract}
\noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{here}. I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code.\vspace{.8cm}
\end{abstract}

\setstretch{1.2}
\clearpage

\renewcommand{\baselinestretch}{0.5}\normalsize
\tableofcontents
\renewcommand{\baselinestretch}{1.1}\normalsize

@@

\hypertarget{why-reproducible-research-in-r}{%
\section{Why reproducible research (in R)?}\label{why-reproducible-research-in-r}}

@@

\hypertarget{prerequesites}{%
\section{Prerequesites}\label{prerequesites}}

@@

\begin{itemize}
\tightlist
\item
  \ldots install \href{https://www.r-project.org/}{R} and \href{https://www.rstudio.com/}{Rstudio} (most recent versions) (R Core Team \protect\hyperlink{ref-R2017}{2017}; RStudio Team \protect\hyperlink{ref-Rstudio2015}{2015}).
\item
  \ldots install \href{https://yihui.name/tinytex/}{tinytex}, a lightweight version of Tex Live (Allaire et al. \protect\hyperlink{ref-markdown2017}{2017}; Xie \protect\hyperlink{ref-tinytex}{2018}\protect\hyperlink{ref-tinytex}{b}).
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \ldots install the packages below using the code below (Sievert et al. \protect\hyperlink{ref-plotly}{2017}; Xie \protect\hyperlink{ref-knitr3}{2014}, \protect\hyperlink{ref-knitr2}{2015}, \protect\hyperlink{ref-bookdown2}{2016}, \protect\hyperlink{ref-bookdown1}{2017}, \protect\hyperlink{ref-knitr1}{2018}\protect\hyperlink{ref-knitr1}{a}; Zhu \protect\hyperlink{ref-kableextra}{2017}).
\end{itemize}

@@

\begin{itemize}
\item
  \ldots download the 5 input files I created --- \texttt{paper.rmd}, \texttt{header.tex}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}. Ignore the other files.
\item
  \ldots learn R and read about the other underlying components namely \href{https://en.wikipedia.org/wiki/Markdown}{Markdown}, \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

\hypertarget{basics-input-and-output-files}{%
\section{Basics: Input and output files}\label{basics-input-and-output-files}}

@@

\begin{itemize}
\tightlist
\item
  \ldots a \texttt{paper.rmd} file (the underlying R Markdown file).
\item
  \ldots a \texttt{header.tex} file (a tex file for document structure).
\item
  \ldots a \texttt{references.bib} file (the bibliography).

  \begin{itemize}
  \tightlist
  \item
    I use paperpile to manage my references and export the \texttt{.bib} file into the folder that contains my \texttt{.rmd} file.
  \end{itemize}
\item
  \ldots a \texttt{data.csv} file (some raw data).
\item
  \ldots{} a \texttt{american-sociological-association.csl} file that defines the style of your bibliography.\footnote{You can download various citation style files from this webpage: \url{https://github.com/citation-style-language/styles}.}
\end{itemize}

@@

\hypertarget{referencing-within-your-document}{%
\section{Referencing within your document}\label{referencing-within-your-document}}

@@

\hypertarget{software-versioning}{%
\section{Software versioning}\label{software-versioning}}

@@

I would recommend to use the command below and simply add it to the appendix as I did here in Appendix \ref{sec:rsessioninfo}. This will make sure you always provide the package versions that you used in the last compilation of your paper. For more advanced tools see \href{https://rstudio.github.io/packrat/}{packrat}.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{cat}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"#"}\NormalTok{, }\KeywordTok{capture.output}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{()), }\StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\DataTypeTok{collapse =}\StringTok{""}\NormalTok{)) }
  \CommentTok{# or use message() instead of cat()}
\end{Highlighting}
\end{Shaded}

\hypertarget{data}{%
\section{Data}\label{data}}

\hypertarget{import}{%
\subsection{Import}\label{import}}

@@

\hypertarget{putting-your-entire-data-into-the-.rmd-file}{%
\subsection{Putting your entire data into the .rmd file}\label{putting-your-entire-data-into-the-.rmd-file}}

@@

\hypertarget{sec:tables}{%
\section{Tables}\label{sec:tables}}

@@

\hypertarget{stargazer-summary-and-regression-tables}{%
\subsection{stargazer(): Summary and regression tables}\label{stargazer-summary-and-regression-tables}}

@@

\hypertarget{kable-and-kable_styling}{%
\subsection{kable() and kable\_styling()}\label{kable-and-kable_styling}}

@@

@@

\caption{\label{tab:tab3}Table with kable() and kablestyling()}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\toprule
  & speed & dist\\
\midrule
\rowcolor{gray!6}  1 & 4 & 2\\
2 & 4 & 10\\
\rowcolor{gray!6}  3 & 7 & 4\\
4 & 7 & 22\\
\rowcolor{gray!6}  5 & 8 & 16\\
\addlinespace
6 & 9 & 10\\
\rowcolor{gray!6}  7 & 10 & 18\\
8 & 10 & 26\\
\rowcolor{gray!6}  9 & 10 & 34\\
10 & 11 & 17\\
\bottomrule
\end{tabu}}
\end{table}

\hypertarget{inline-code-results}{%
\section{Inline code \& results}\label{inline-code-results}}

@@

\hypertarget{figures}{%
\section{Figures}\label{figures}}

\hypertarget{r-base-graphs}{%
\subsection{R base graphs}\label{r-base-graphs}}

@@

\hypertarget{ggplot2-graphs}{%
\subsection{ggplot2 graphs}\label{ggplot2-graphs}}

@@

\hypertarget{good-practices}{%
\section{Good practices}\label{good-practices}}

@@

  \begin{itemize}
  \tightlist
  \item
    Main file with text/code: ``paper.rmd'', ``report.rmd''
  \item
    Data files: "data\_xxxxxx.*"
  \item
    Image files: "fig\_xxxxxx.*"
  \item
    Tables files: "table\_xxxx.*"
  \item
    etc.
  \item
    Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called \texttt{fig\_1\_xxxxx.pdf}.
  \end{itemize}
\item
  Use the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
\item
  Name rchunks according to what they do or produce:

@@

\hypertarget{citation-styles}{%
\section{Citation styles}\label{citation-styles}}

@@

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\hypertarget{sec:rsessioninfo}{%
\subsection{Attach R session info in appendix}\label{sec:rsessioninfo}}

Since R and R packages are constantly evolving you might want to add the R session info that contains information on the R version as well as the packages that are loaded.

\begin{verbatim}
## R version 3.6.2 (2019-12-12)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## Running under: Windows 10 x64 (build 17763)
## 
## Matrix products: default
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.2.1    kableExtra_1.1.0 knitr_1.26       stargazer_5.2.2 
## 
## loaded via a namespace (and not attached):
##  [1] Rcpp_1.0.3        pillar_1.4.3      compiler_3.6.2    tools_3.6.2      
##  [5] digest_0.6.23     evaluate_0.14     tibble_2.1.3      lifecycle_0.2.0  
##  [9] gtable_0.3.0      viridisLite_0.3.0 pkgconfig_2.0.3   rlang_0.4.5      
## [13] rstudioapi_0.10   yaml_2.2.0        xfun_0.11         withr_2.1.2      
## [17] dplyr_0.8.3       httr_1.4.1        stringr_1.4.0     xml2_1.2.2       
## [21] vctrs_0.2.4       hms_0.5.2         tidyselect_0.2.5  webshot_0.5.2    
## [25] grid_3.6.2        glue_1.3.2        R6_2.4.1          rmarkdown_2.0    
## [29] bookdown_0.16     farver_2.0.1      purrr_0.3.3       readr_1.3.1      
## [33] magrittr_1.5      scales_1.1.0      htmltools_0.4.0   assertthat_0.2.1 
## [37] rvest_0.3.5       colorspace_1.4-1  labeling_0.3      stringi_1.4.3    
## [41] lazyeval_0.2.2    munsell_0.5.0     crayon_1.3.4
\end{verbatim}

\hypertarget{all-the-code-in-the-paper}{%
\subsection{All the code in the paper}\label{all-the-code-in-the-paper}}

@@

\KeywordTok{print}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{(), }\DataTypeTok{local =} \OtherTok{FALSE}\NormalTok{)}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-markdown2017}{}%
Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017. \emph{Markdown: 'Markdown' Rendering for R}.

\leavevmode\hypertarget{ref-hlavac2013stargazer}{}%
Hlavac, Marek. 2013. ``Stargazer: LaTeX Code and Ascii Text for Well-Formatted Regression and Summary Statistics Tables.'' \emph{URL: Http://CRAN. R-Project. Org/Package= Stargazer}.

\leavevmode\hypertarget{ref-Kirsop2005-ro}{}%
Kirsop, Barbara and Leslie Chan. 2005. ``Transforming Access to Research Literature for Developing Countries.'' \emph{Serials Review} 31(4):246--55.

\leavevmode\hypertarget{ref-R2017}{}%
R Core Team. 2017. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing.

\leavevmode\hypertarget{ref-Rstudio2015}{}%
RStudio Team. 2015. \emph{RStudio: Integrated Development Environment for R}. Boston, MA: RStudio, Inc.

\leavevmode\hypertarget{ref-plotly}{}%
Sievert, Carson, Chris Parmer, Toby Hocking, Scott Chamberlain, Karthik Ram, Marianne Corvellec, and Pedro Despouy. 2017. \emph{Plotly: Create Interactive Web Graphics via 'Plotly.js'}.

\leavevmode\hypertarget{ref-knitr3}{}%
Xie, Yihui. 2014. ``Knitr: A Comprehensive Tool for Reproducible Research in R.'' in \emph{Implementing reproducible computational research}, edited by V. Stodden, F. Leisch, and R. D. Peng. Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-knitr2}{}%
Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-bookdown2}{}%
Xie, Yihui. 2016. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}. Boca Raton, Florida: Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-bookdown1}{}%
Xie, Yihui. 2017. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}.

\leavevmode\hypertarget{ref-knitr1}{}%
Xie, Yihui. 2018a. \emph{Knitr: A General-Purpose Package for Dynamic Report Generation in R}.

\leavevmode\hypertarget{ref-tinytex}{}%
Xie, Yihui. 2018b. \emph{Tinytex: Helper Functions to Install and Maintain 'Tex Live', and Compile 'Latex' Documents}.

\leavevmode\hypertarget{ref-kableextra}{}%
Zhu, Hao. 2017. \emph{KableExtra: Construct Complex Table with 'Kable' and Pipe Syntax}.
